Drawing Math

### 2022-05-12 paper/Paper.tex
some questions

% TODO: ask closure question
% TODO: show result that if $(s_{a}^1, ... ) = (s_{b}^1,...)$ then $b-a$ is a period for the state
% and Delta p_a = p_b and is thus invariant under mod b-a. So, if Delta p_{b-a} \neq 0 
% we have that the turtle will not move in a closed shape. If Delta p_{b-a} = 0, it will

@@

\begin{remark}[Complexity]
  For $d > 2$, prime, and coprime to $b$, we can find $\digSumPeriodic$
  in polytime by multiplying $(b - 1) \cdot \frac{d-1}{2} \mod b$ \cite{OnDecSeq}. The authors are unsure
  as to the complexity of finding $\digSumPeriodic$ otherwise.
\end{remark}

@@

\begin{remark}[Randomness assumption]
  The randomness assumption, that $(\digSumPeriodicNoJ^1, ..., \digSumPeriodicNoJ^k)$
  is drawn from a random distribution is very much not true. But, given a rational parameter
  there does seem to be some element of randomness for $\digSumPeriodic$. See \cite{OnDecSeq} for more information.
\end{remark}
\section{Open Questions}

>>>>

@@

\begin{remark}[Complexity]
\label{remark:digsum-complexity}
  For $d > 2$, prime, and coprime to $b$, we can find $\digSumPeriodic$
  in polytime by multiplying $(b - 1) \cdot \frac{d-1}{2} \mod b$ \cite{OnDecSeq}. The authors are unsure
  as to the complexity of finding $\digSumPeriodic$ otherwise.
\end{remark}

@@

\begin{remark}[Randomness assumption]
\label{remark:digSumRandomness}
  The randomness assumption, that $(\digSumPeriodicNoJ^1, ..., \digSumPeriodicNoJ^k)$
  is drawn from a random distribution is very much not true. But, given a rational parameter
  there does seem to be some element of randomness for $\digSumPeriodic$. See \cite{OnDecSeq} for more information.
\end{remark}

\section{Open Questions and Future Work}
A whole host of questions naturally arise from this problem. We will proceed to list
the ones which immediately stand out. For a complete list of open problems, which have
been solved, and the associated (financial) reward to each question, see our website
::::TODO::::
\begin{enumerate}
  \item \textbf{Periodic Digit Sum in NP?}: As far as the authors are aware, given 
  any rational number, $\frac{n}{d}$ in a fixed base $b$, is finding the sum of the digits in
  one period modulo $b$ in $NP$? I.e. could one give a poly-size
  certificate to a poly-time verifier which verifies if a digital sum equals $\sigma \in \Z_b$?
  The size of the input is the number of bits required to describe $\frac{n}{d}$. The authors 
  feel that intuitively the answer should be yes. A certificate could potentially be related
  to the factors of the denominator and the period length. I.e.\ we know how to find
  the periodic digital sum of a prime in polynomial time (see \ref{remark:digsum-complexity}). So,
  could we somehow use this in combination with a prime factorization?

  \item \textbf{Closure in NP or CoNP?}: For fixed bases of size $b$, is closure in NP of CoNP?
  I.e.\ is there is a poly-sized certificate and poly-time verifier which can prove or disprove
  that $D-1$ rationals draw a closed shape? The author's are uncertain here but conjecture
  may be in CoNP. Either a gadget based reduction or a direct algorithm to generate a valid
  certificate suffice to answer this question.

  \item \textbf{Distribution }: Given a random rational number $\frac{n}{d}$
  where $n \sim \Z_q$ and $d \sim \Z_q$ for some fixed $q \in \N$, what is the distribution
  of $\sigma$, the periodic digital sum modulo base $b$? Specifically, is the distribution
  indistinguishable (TODO: cite meaning) from the uniform distribution of $\Z_b$? 
  See remark \ref{remark:digSumRandomness} for an application of this result.

  \item \textbf{Decomposition}: This one is totally out of left field. From our analysis,
  it seems as if using rational numbers to draw out shapes has a lot of underlying complexity
  but also a lot of structure. The authors were wondering if given any closed shape $\ell$ which
  can be described with $n$ bits, could poly-n bits be used in combination with the rational
  sequence drawing algorithm described throughout this paper as description of $\ell$.
  In other words, could some sort of ``Fourier Transform" be done between an explicitly described
  closed shape and a sequence of rationals? We are also interested whether $1 - \epsilon$
  approximation exists 
  (where the approximation ``goodness" could be measured as a function of
  average distance from the original line to the line generated via the sequence of rationals).

\end{enumerate}
